Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-09 demystify.tex
updates

\begin{table}
  \centering
  \footnotesize
  \caption{Different types of PhD funding}\label{tab:funding}
  \begin{tabular}{c|c|c|c}
    \toprule
    &\textbf{TA}&\textbf{RA}&\textbf{Fellowship}\\
    \midrule
    \textbf{From} & School & Profs. & School/External\\
    \textbf{For}                  & Teaching Assistant       & Research                        & Research                              \\
    \textbf{Tuition/Ins./Stipend} & Yes                      & Yes                             & Yes                                   \\
    \textbf{Cover Summer?}              & No                       & Maybe                           & Yes                                   \\
    \midrule
    \textbf{Pros}                 & Research Freedom         & Get to do research              & Research Freedom                      \\
    \textbf{Cons}                 & Teaching Duties, Uncertain            & Research Restriction, Uncertain & Competitive, Limited             \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \footnotesize
  \caption{Different types of PhD funding. All Covered: includes tuition, insurance, and stipend.}\label{tab:funding}
  \begin{tabular}{c|c|c|c}
    \toprule
    &\textbf{TA}&\textbf{RA}&\textbf{Fellowship}\\
    \midrule
    \textbf{From} & School & Profs. & School/External\\
    \textbf{For}                  & Teaching Assist.       & Research                        & Research                              \\
    \textbf{Cover All?} & Yes                      & Yes                             & Yes                                   \\
    \textbf{Summer?}              & No                       & Maybe                           & Yes                                   \\
    \midrule
    \textbf{Pros}                 & Research Freedom         & Get to do research              & Research Freedom                      \\
    \textbf{Cons}                 & Teaching Duties           & Research Restriction & Competitive, Limited             \\
    \bottomrule
  \end{tabular}
\end{table}
